Stochastic Convolutional Sparse Coding

### 2018-10-25 cvpr2019/supplement.tex
add paper

%\part*{Supplementary Material\\ Stochastic Convolutional Sparse Coding}

@@

\begin{figure}[h]
\begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/iteVSobj-city.pdf}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/timeVSobj-city.pdf}
\end{subfigure}

\begin{subfigure}{0.48\textwidth}
  \includegraphics[width=1\linewidth]{figure/batchCity100.pdf}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
  \includegraphics[width=1\linewidth]{figure/heideCity100.pdf}
\end{subfigure}
\vspace{0.2cm}

    \resizebox{1\linewidth}{!}{
        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
            \cline{1-11}
            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
            \hline
            PSNR~\cite{heide2015fast} & 29.67 & \textbf{28.14} & 29.58 & 29.69 & 28.74 & 29.43 & 27.89  & 30.13 & 27.03 & 30.61 \\
            \hline
            PSNR ours & \textbf{29.78} & \textbf{28.14} & \textbf{29.67}  & \textbf{29.85} & \textbf{28.88} & \textbf{29.95} & \textbf{27.97} & \textbf{30.37} & \textbf{27.14} & \textbf{30.89} \\
            \hline
        \end{tabular} }

\caption{Experimental results obtained on the city dataset. Top: Convergence comparison between the-state-of-art batch method~\cite{heide2015fast} and SBCSC with different subsampling probability. Middle: Learned filters by SBCSC with $p=0.1$ and the comparable method. Even though these dictionaries look similar, our method learns more smooth filters. Compared to the learned filters in Fig.\ \ref{fig:subsampleResult}, they have different representations of the dictionaries, where data-specific features are learned from handful training images. Bottom: Numerical comparisons of the reconstruction quality obtained by the presented filters.}
\label{fig:subsampleResult-city}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
\end{subfigure}

\caption{Experimental results obtained on city dataset. Left: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}. Right: Testing PSNR with respect to execution time.}
\label{fig:onlineSmall-city}
\end{figure}

@@

\begin{figure}[h]
\centering
  \includegraphics[width=0.7\linewidth]{figure/heide400-supple.pdf}
  \includegraphics[width=0.7\linewidth]{figure/online400-supple.pdf}
  \vspace{0.2cm}

    \resizebox{1\linewidth}{!}{
        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
            \cline{1-11}
            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
            \hline
            PSNR~\cite{heide2015fast} & 29.60 & 28.11 & 29.47 & 28.98 & 28.79 & 29.21 & 28.03  & 29.31 & 27.42 & 30.52 \\
            \hline
            PSNR ours & \textbf{30.24} & \textbf{28.34} & \textbf{29.95}  & \textbf{30.30} & \textbf{29.43} & \textbf{29.96} & \textbf{28.24} & \textbf{30.57} & \textbf{27.72} & \textbf{31.67} \\
            \hline
        \end{tabular} }
  \caption{ Visual and numerical comparisons between the learned over-complete dictionaries by batch-mode algorithm and by online-mode algorithm. Top: Over-complete dictionary learned by batch CSC model~\cite{heide2015fast} on small dataset, and proposed online CSC model (SOCSC) on large dataset. Bottom: Respective reconstruction quality for these two over-complete dictionaries.}
  \label{fig:overCompleteDic-dataset}
\end{figure}

>>>>

\begin{strip}
\begin{center}
{\Large \bf Stochastic Convolutional Sparse Coding \\ Supplementary Material }
\end{center}
\end{strip}

\section{Solvers for LASSO and QCQP}
Algorithm~\ref{algo:ADMMLasso} is used to optimize a LASSO problem in the following form:
\begin{equation}
    \minimize{\code} \frac{1}{2}\|\signal - \Filter \code \|_2^2 + \lambda\| \code \|_1
\end{equation}

\begin{algorithm}
\caption{ADMM framework for solving LASSO} \label{algo:ADMMLasso}
\begin{algorithmic}[1]
    \For{$s=1$ to $S$}
        \State // z-update step (quadratic programming)
        \State $\code^{s+1} \gets (\Filter ^ \top \Filter + \rho \Id )^{-1}(\Filter^\top \signal + \rho(\Vector{y}^s - \Vector{q}^s ) )$
        \State // y-update step (soft thresholding)
        \State $\Vector{y}^{s+1} \gets (\code^{s+1}+\Vector{q}^{s} - \frac{\lambda}{\rho})_{+} ~ - ~ (-\code^{s+1}-\Vector{q}^{s} - \frac{\lambda}{\rho})_{+}$
        \State // scaled dual variables update
        \State $\Vector{q}^{s+1} \gets \bold{q}^{s}+\code^{s+1}-\Vector{y}^{s+1}$
    \EndFor
\end{algorithmic}
\end{algorithm}
$S$ is the total number of ADMM iteration. $\Vector{y}$ is the introduced slack variable, $\Vector{q}$ is the scaled dual variable, and $\rho$ is the augmented Lagrangian penalty.

Algorithm~\ref{algo:BCDQCQP} is used to optimize a QCQP problem in the following form:
\begin{equation}
\begin{split}
    \minimize{\filter} & \frac{1}{2}\|\signal - \Code \filter \|_2^2 \\
    \text{subject to} & ~ \|\filter_k\|^2_2 \leq 1 ~~ \forall k \in \{1,\dots,K\},
\end{split}
\end{equation}

\begin{algorithm}
\caption{Projected Block Coordinate Descent for solving QCQP} \label{algo:BCDQCQP}
\begin{algorithmic}[1]
\State $\Vector{r} \gets \signal - \Code \filter $
\While {not converge}
    \For{$k=1$ to $K$}
        \State $ \filter^{\ast}_k \gets \filter_k + \Code_k ^ \top \Vector{r} ~ / ~ L_k $
        \State $ \filter^{\ast}_k \gets \filter^{\ast}_k ~ / ~ \text{max}( \|\filter^{\ast}_k\|,1 ) $
        \State $ \Vector{r} ~~ \gets \Vector{r} + \Code_k( \filter_k - \filter^{\ast}_k ) $
    \EndFor
    \State  $ \filter \gets \filter^{\ast} $
\EndWhile
\end{algorithmic}
\end{algorithm}
$L_k$ is the Lipschitz constant of $\Code_k^\top \Code_k$.

@@

\begin{figure}[h]
\centering
\begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
\end{subfigure}

\caption{Experimental results obtained on city dataset. Top: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach~\cite{liu-2018-first}. Bottom: Testing PSNR with respect to execution time.}
\label{fig:onlineSmall-city}
\end{figure}

\begin{figure*}[h]
\begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/iteVSobj-city.pdf}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/timeVSobj-city.pdf}
\end{subfigure}

\centering
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/batchCity100.pdf}
\end{subfigure}
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/heideCity100.pdf}
\end{subfigure}
\vspace{0.2cm}

    \resizebox{0.8\linewidth}{!}{
        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
            \cline{1-11}
            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
            \hline
            PSNR~\cite{heide2015fast} & 29.67 & \textbf{28.14} & 29.58 & 29.69 & 28.74 & 29.43 & 27.89  & 30.13 & 27.03 & 30.61 \\
            \hline
            PSNR ours & \textbf{29.78} & \textbf{28.14} & \textbf{29.67}  & \textbf{29.85} & \textbf{28.88} & \textbf{29.95} & \textbf{27.97} & \textbf{30.37} & \textbf{27.14} & \textbf{30.89} \\
            \hline
        \end{tabular} }

\caption{Experimental results obtained on the city dataset. Top: Convergence comparison between the-state-of-art batch method~\cite{heide2015fast} and SBCSC with different subsampling probability. Middle: Learned filters by SBCSC with $p=0.1$ and the comparable method. Even though these dictionaries look similar, our method learns more smooth filters. Compared to the learned filters in Fig.\ \ref{fig:subsampleResult}, they have different representations of the dictionaries, where data-specific features are learned from handful training images. Bottom: Numerical comparisons of the reconstruction quality obtained by the presented filters.}
\label{fig:subsampleResult-city}
\end{figure*}

@@

@@

\begin{figure*}[h]
\centering
  \begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/heide400-supple.pdf}
  \end{subfigure}
  \vspace{0.2cm}
  \begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/online400-supple.pdf}
  \end{subfigure}
  \vspace{0.2cm}

    \resizebox{0.8\linewidth}{!}{
        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
            \cline{1-11}
            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
            \hline
            PSNR~\cite{heide2015fast} & 29.60 & 28.11 & 29.47 & 28.98 & 28.79 & 29.21 & 28.03  & 29.31 & 27.42 & 30.52 \\
            \hline
            PSNR ours & \textbf{30.24} & \textbf{28.34} & \textbf{29.95}  & \textbf{30.30} & \textbf{29.43} & \textbf{29.96} & \textbf{28.24} & \textbf{30.57} & \textbf{27.72} & \textbf{31.67} \\
            \hline
        \end{tabular} }
  \caption{ Visual and numerical comparisons between the learned over-complete dictionaries by batch-mode algorithm and by online-mode algorithm. Top: Over-complete dictionary learned by batch CSC model~\cite{heide2015fast} on small dataset, and proposed online CSC model (SOCSC) on large dataset. Bottom: Respective reconstruction quality for these two over-complete dictionaries.}
  \label{fig:overCompleteDic-dataset}
\end{figure*}
